---
title: "Assignment 2"
author: "Maninderpreet Singh Puri"
date: "21/10/2020"
output: html_document
---

Task 1 of 2: Correlation

1). Missing Values:

Importing Libraries
```{r}
library(tidyr)
library(dplyr)
library(datasets)
library(tidyverse)
library(ggpubr)
```

Reading Data
```{r}
mdata = read.csv("Movie.csv")#load data
glimpse(mdata)#data has 26 columns and 3891 rows
```
I am selecting the variables of interest and dropping variables that are not of interest(attributes about structure). This will process the variables which are important for movie evaluation.
```{r}
mdata = mdata[,c(3,5,9,13,14,21,24,26)]
```

Identifying NA values in remaining columns
```{r}
missing_Reviews <- sum(is.na(mdata$Reviews))
missing_Reviews# 1 NA values
missing_Director_facebook_likes <- sum(is.na(mdata$Director_facebook_likes))
missing_Director_facebook_likes# 0 NA values
missing_Gross <- sum(is.na(mdata$Gross))
missing_Gross# 0 NA values
missing_Votes <- sum(is.na(mdata$Votes))
missing_Votes# 0 NA values
missing_Cast_total_facebook_likes <- sum(is.na(mdata$Cast_total_facebook_likes))
missing_Cast_total_facebook_likes# 0 NA values
missing_Content_rating <- sum(is.na(mdata$Content_rating))
missing_Content_rating# 0 NA values
missing_Budget <- sum(is.na(mdata$Budget))
missing_Budget# 0 NA values
missing_Imdb_score <- sum(is.na(mdata$Imdb_score))
missing_Imdb_score# 0 NA values
missing_Movie_facebook_likes <- sum(is.na(mdata$Movie_facebook_likes))
missing_Movie_facebook_likes# 0 NA values
```

As the number of missing values is just 1, so we can drop that row.
```{r}
mdata <- na.omit(mdata)
```



2) Exploration:

Adding Profit column
```{r}
Profit <- mdata$Gross - mdata$Budget
mdata$Profit= Profit
```

Normalizing data in all variables
```{r}
mdata$Reviews <-(mdata$Reviews - min(mdata$Reviews)) /(max(mdata$Reviews)-min(mdata$Reviews))

mdata$Director_facebook_likes <-(mdata$Director_facebook_likes - min(mdata$Director_facebook_likes))/(max(mdata$Director_facebook_likes)-min(mdata$Director_facebook_likes))

mdata$Gross <-(mdata$Gross - min(mdata$Gross)) /(max(mdata$Gross)-min(mdata$Gross))

mdata$Votes <-(mdata$Votes - min(mdata$Votes)) /(max(mdata$Votes)-min(mdata$Votes))

mdata$Cast_total_facebook_likes <-(mdata$Cast_total_facebook_likes - min(mdata$Cast_total_facebook_likes)) /(max(mdata$Cast_total_facebook_likes)-min(mdata$Cast_total_facebook_likes))

mdata$Budget <-(mdata$Budget - min(mdata$Budget)) /(max(mdata$Budget)-min(mdata$Budget))

mdata$Imdb_score <-(mdata$Imdb_score - min(mdata$Imdb_score)) /(max(mdata$Imdb_score)-min(mdata$Imdb_score))

mdata$Movie_facebook_likes <-(mdata$Movie_facebook_likes - min(mdata$Movie_facebook_likes)) /(max(mdata$Movie_facebook_likes)-min(mdata$Movie_facebook_likes))

mdata$Profit <-(mdata$Profit - min(mdata$Profit)) /(max(mdata$Profit)-min(mdata$Profit))

```

Relationship between Profit and other variables.
The trend line shows the relationship is positive, negative or there is no relation.
```{r}
ggscatter(mdata, x = "Reviews", y = "Profit", fill = "lightgray", shape = 4,
size = 2, color = "#00AFBB", add = c("reg.line")) 
ggscatter(mdata, x = "Director_facebook_likes", y = "Profit", fill = "lightgray", shape = 4, size = 2, color = "Cyan", add = c("reg.line"))
ggscatter(mdata, x = "Gross", y = "Profit", fill = "lightgray", shape = 4,
size = 2, color = "#E7B800", add = c("reg.line"))
ggscatter(mdata, x = "Votes", y = "Profit", fill = "lightgray", shape = 4,
size = 2, color = "#FC4E07", add = c("reg.line"))
ggscatter(mdata, x = "Cast_total_facebook_likes", y = "Profit", fill = "lightgray", shape = 4, size = 2, color = "Blue", add = c("reg.line"))
ggscatter(mdata, x = "Budget", y = "Profit", fill = "lightgray", shape = 4,
size = 2, color = "Red", add = c("reg.line"))
ggscatter(mdata, x = "Imdb_score", y = "Profit", fill = "lightgray", shape = 4,
size = 2, color = "Green", add = c("reg.line"))
ggscatter(mdata, x = "Movie_facebook_likes", y = "Profit", fill = "lightgray", shape = 4, size = 2, color = "Black", add = c("reg.line"))
```

Calculating correlation between the variable(s) used in the Data set.
```{r}
res4 <- cor(mdata, use = "everything", method = c("kendall")) 
round(res4, 2)
```

Listing and plotting Strong and Weak Correlations
```{r}
library(corrplot)
cr = cor(mdata)
corrplot(cr)
corrplot(cr, method = "color")
corrplot(cr, method = "pie")
```
As we can see in the plot the {Budget, Profit} and {Budget, Imdb_score} pairs have weak correlation. Rest all have a positive correlation(strong correlation). 
This means as Budget increases, the Profit and Imdb_score decreases.




Task 2 of 2: Association Rule mining

Importing Libraries
```{r}
library(arules)
library(arulesViz)
```

Reading data
```{r}
tdata = read.csv("Titanic.csv")#load data
glimpse(tdata)#data has 5 columns and 2201 rows
class(tdata)
head(tdata)
```

Calculating missing values
```{r}
missing_titanic <- sum(is.na(tdata))
missing_titanic# No missing values in Titanic dataset
```
No imputation is needed as we have to perform association rule mining which doesn't need numeric values.

Sub setting data to eliminate the first index column
```{r}
tdata<- subset(tdata,select = -c(X))
head(tdata)
summary(tdata)
```

Converting to Transaction data
```{r}
tdata <- as (tdata, "transactions")
```

Creating the Association rules using apriori algorithm
```{r}
rules_Survived_Yes <- apriori(tdata, parameter = list(sup = 0.005, conf = 0.8, minlen = 2), appearance = list(default = "lhs", rhs ="Survived=Yes" ))
summary(rules_Survived_Yes)
```

Inspecting the top 3 pairs by Lift 
```{r}
inspect(head(sort(rules_Survived_Yes, by="lift"),3))
```
The three pairs of entries have the highest lift value. 

Plotting the top 3 pairs by Lift 
```{r}
datadd <- head(sort(rules_Survived_Yes, by="lift"),n = 3)
head(quality(datadd))
plot(datadd)
plot(datadd , method = "graph", engine = "htmlwidget")
```

There is a significant difference between children traveling in first class, second class and third class.

According the generated graph, children who are traveling in first class and are female {Class=1st, Sex=Female} => {Survived=Yes} survived the tragedy. Also children who are in second class {Class=2nd, Age=Child} => {Survived=Yes} and were females {Class=2nd, Sex=Female, Age=Child} => {Survived=Yes} survived as well.

However children in third class did not survived according the generated graph.

One of the value added observations that can be derived from above information is that the first-class female passengers and Second-class children had the same chance of survival(high survival chance) than men in First, second, third class(low survival chance).


